---
title: "Data Dictionary"
output: 
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Power Law Process (PLP)

```{r}
plp = readRDS('PLP.rds')
str(plp)
```

- `N`: The total number of events
- `K`: The total number of predictor variables
- `S`: The total number of shifts,
- `D`: The total number of drivers,
- `id`: The index of driver ID for different shifts
- `tau`: The length of each shift (excluding break rest time)
- `event_time`: Time to each event
- `group_size`: The number of events in each shift
- `X_predictors`: The predictor variable matrix

\clearpage

# Jump Power Law Process (JPLP)

```{r}
jplp = readRDS('JPLP.rds')
str(jplp)
```

- `N`: The total number of events
- `K`: The total number of predictor variables
- `S`: The total number of shifts,
- `D`: The total number of drivers,
- `id`: The index of driver ID for different shifts
- `r_trip`: The index of different segments
- `t_trip_start`: The start time of different segments
- `t_trip_end`: The end time of different segments
- `event_time`: Time to each event
- `group_size`: The number of events in each shift
- `X_predictors`: The predictor variable matrix